Ultrafast

### 2023-07-29 manuscript/manuscript.qmd
Update

---
author: 
  - name: "Kjell Jorner"
    orcid: 0000-0002-4191-6790
    email: "kjell.jorner@chem.ethz.ch"
    corresponding: true
    affiliations: 
      - ref: eth
      - ref: chalmers
      - ref: toronto-chem
      - ref: toronto-cs
  - name: "Robert Pollice"
    orcid: 0000-0001-8836-6266
    affiliations: 
      - ref: rug
      - ref: toronto-chem
      - ref: toronto-cs  
  - name: "Cyrille Lavigne"
    orcid: 0000-0003-2778-1866
    affiliations: 
      - ref: toronto-chem
      - ref: toronto-cs    
  - name: "Alán Aspuru Guzik"
    orcid: 0000-0002-8277-4434
    affiliations:
      - ref: toronto-chem
      - ref: toronto-cs
      - ref: toronto-chem-eng
      - ref: toronto-mat-eng
      - ref: vector
      - ref: ac

@@

![Write some text here]({{< var fig_local_azaphenalenes >}}.pdf){#fig-local-azaphenalenes}

```{python}
# | label: tbl-local-azaphenalenes
# | tbl-cap: Astronomical object
# | echo: false
import pandas as pd
from IPython.display import display, Markdown

@@

![Here's some more text]({{< var fig_local_azulenes >}}.pdf){#fig-local-azulenes}

```{python}
# | label: tbl-local-azulenes
# | tbl-cap: Astronomical object
# | echo: false
import pandas as pd
from IPython.display import display, Markdown

@@

![Write some text here]({{< var fig_global_all_gaps >}}.pdf){#fig-global-all-gaps}

```{python}
# | label: tbl-global-all
# | tbl-cap: Astronomical object
# | echo: false
import pandas as pd
from IPython.display import display, Markdown

@@

![Write some text here]({{< var fig_garner_gaps >}}.pdf){#fig-garner-gaps}

```{python}
# | label: tbl-garner-gaps
# | tbl-cap: Astronomical object
# | echo: false
import pandas as pd
from IPython.display import display, Markdown

@@

![Singlet-triplet gap split by scaffold for the rationally designed dataset *vs.* the reference level.]({{< var fig_global_scaffolds_gaps >}}.png){#fig-global-scaffolds-gaps}

@@

![Singlet-triplet gaps with CIS + DSP and linear correction for the (a) azaphenalenes and (b) azaazulenes *vs.* the reference level.]({{< var fig_local_corr >}}.pdf){#fig-local-corr}

>>>>

---
author: 
  - name: "Kjell Jorner"
    orcid: 0000-0002-4191-6790
    email: "kjell.jorner@chem.ethz.ch"
    corresponding: true
    affiliations: 
      - ref: eth
      - ref: chalmers
      - ref: toronto-chem
      - ref: toronto-cs
  - name: "Robert Pollice"
    orcid: 0000-0001-8836-6266
    email: "r.pollice@rug.nl"
    corresponding: true
    affiliations: 
      - ref: rug
      - ref: toronto-chem
      - ref: toronto-cs  
  - name: "Cyrille Lavigne"
    orcid: 0000-0003-2778-1866
    affiliations: 
      - ref: toronto-chem
      - ref: toronto-cs    
  - name: "Alán Aspuru Guzik"
    orcid: 0000-0002-8277-4434
    affiliations:
      - ref: toronto-chem
      - ref: toronto-cs
      - ref: toronto-chem-eng
      - ref: toronto-mat-eng
      - ref: vector
      - ref: ac

@@

![Excitation properties for azaphenalenes _vs._ the reference level. (a) Singlet excitation energies. (b) Triplet excitation energies. (c) Oscillator strengths. (d) Singlet-triplet energy gaps with CIS. (e) Singlet-triplet energy gaps with SCF + DSP. (f) Singlet-triplet energy gaps with CIS + DSP.]({{< var fig_local_azaphenalenes >}}.pdf){#fig-local-azaphenalenes}

```{python}
# | label: tbl-local-azaphenalenes
# | tbl-cap: Metrics for azaphenalenes.
# | echo: false
import pandas as pd
from IPython.display import display, Markdown

@@

![Excitation properties for azaazulenes _vs._ the reference level. (a) Singlet excitation energies. (b) Triplet excitation energies. (c) Oscillator strengths. (d) Singlet-triplet energy gaps with CIS. (e) Singlet-triplet energy gaps with SCF + DSP. (f) Singlet-triplet energy gaps with CIS + DSP.]({{< var fig_local_azulenes >}}.pdf){#fig-local-azulenes}

```{python}
# | label: tbl-local-azulenes
# | tbl-cap: Metrics for azaazulenes.
# | echo: false
import pandas as pd
from IPython.display import display, Markdown

@@

![Singlet-triplet energy gaps for rationally design set _vs._ reference level for (a) SCF + DSP, (b) CIS + DSP and (c) CIS + DSP and linear correction.]({{< var fig_global_all_gaps >}}.pdf){#fig-global-all-gaps}

```{python}
# | label: tbl-global-all
# | tbl-cap: Metrics for rationally designed set.
# | echo: false
import pandas as pd
from IPython.display import display, Markdown

@@

![Singlet-triplet energy gaps for CIS + DSP and linear correction _vs._ reference level for the subsets of (a) non-alternants (b) non-alternants constrained to higher symmetry and (c) substituted non-alternants. Compounds contained in the rationally designed sets are marked with dashed circles and those with negative triplet excitation energies are marked with a semi-transparent red circle.]({{< var fig_garner_gaps >}}.pdf){#fig-garner-gaps}

```{python}
# | label: tbl-garner-gaps
# | tbl-cap: Metrics for the dataset from Garner _et al._
# | echo: false
import pandas as pd
from IPython.display import display, Markdown

@@

![Singlet-triplet energy gaps split by scaffold for the rationally designed dataset *vs.* the reference level.]({{< var fig_global_scaffolds_gaps >}}.png){#fig-global-scaffolds-gaps}

@@

![Singlet-triplet energy gaps with CIS + DSP and linear correction for the (a) azaphenalenes and (b) azaazulenes *vs.* the reference level.]({{< var fig_local_corr >}}.pdf){#fig-local-corr}
